MSHS COVID-19 Vaccination Summary

### 2022-10-04 MSHS Vaccines Administered Hybrid Data Model.Rmd
Update code to reflect updated shared drive folder structure.

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

  # Import schedule repository daily summary for 2020 and 2021
  sched_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Repo Sched & Admin Data",
           "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

  # Import vaccine administration repository daily summary for Jan-Jun 2022
  vax_admin_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Repo Sched & Admin Data",
           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-09-14.RDS"))

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
} else {

  # Select repository
  repo_file <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report",
             "/*.*"),
    caption = "Select hybrid vaccine administration repository.")

@@

  # Select most recent weekly file
  weekly_vax_admin <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report",
             "/Weekly Automated Reports/*.*"),
    caption = "Select weekly vaccine administration data.")

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

>>>>

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Sched & Admin Reporting",
  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

  # Import schedule repository daily summary for 2020 and 2021
  sched_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

  # Import vaccine administration repository daily summary for Jan-Jun 2022
  vax_admin_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-10-04.RDS"))

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, 
                              "/Hybrid Sched & Admin Reporting",
                              "/Hybrid Model Repo",
                              "/Hybrid Vaccine Admin Data ",
                              format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                              format(max(hybrid_repo$Date), "%m%d%y"),
                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
} else {

  # Select repository
  repo_file <- choose.files(
    default = 
      paste0(user_directory,
             "/Hybrid Sched & Admin Reporting",
             "/Hybrid Model Repo",
             "/*.*"),
    caption = "Select hybrid vaccine administration repository.")

@@

  # Select most recent weekly file
  weekly_vax_admin <- choose.files(
    default = 
      paste0(user_directory,
             "/Hybrid Sched & Admin Reporting",
             "/Vaccine Admin Reports/*.*"),
    caption = "Select weekly vaccine administration data.")

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory,
                              "/Hybrid Sched & Admin Reporting",
                              "/Hybrid Model Repo",
                              "/Hybrid Vaccine Admin Data ",
                              format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                              format(max(hybrid_repo$Date), "%m%d%y"),
                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
